Andres Karjus

### 2018-08-31 index.Rmd
paper link

- "Two problems and solutions in evolutionary corpus-based language dynamics research" to be presented @ SLE 2018: [slides](https://andreskarjus.github.io/sle_tallinn_languagedynamics) with interactive plots and [code](https://github.com/andreskarjus/sle_tallinn_languagedynamics) now available.

>>>>

- "Two problems and solutions in evolutionary corpus-based language dynamics research" presented @ SLE 2018: [slides](https://andreskarjus.github.io/sle_tallinn_languagedynamics) with interactive plots and [code](https://github.com/andreskarjus/sle_tallinn_languagedynamics) now available. Full paper on topical advection (the 2nd half of the talk) available [here](https://arxiv.org/abs/1806.00699).
